---
title: "Analyzing the Number of Marriage Licenses Before and After Covid"
author: 
  - Yisu Hou
date: today
date-format: long
abstract: "Abstract: There is a lack of research regarding the effects of Covid-19 on
the number of marriages. As we know, Covid-19 travel lockdowns prevented
individuals from socializing, so it is more difficult to meet new people and 
maintain existing romantic relationships. We believe this may be reflected
with a reduction in marriages during the Covid."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

cleaned_data <- read_csv(here::here("data/cleaned_data.csv"))

```


# Graph

```{r}
#| echo: false

cleaned_data %>% ggplot(aes(x = date, y = marriage_licenses)) + 
  geom_point() + 
  labs(title = "Figure 1: Marriage Licenses Before and After Covid",
       x = "Date (Year)", y = "Number of Licenses")
```
&nbsp;&nbsp; Observing Figure 1, we can observe that the number of marriage licenses did not
decrease after Covid-19. In fact, the data shows an increases in the peak values
after the pandemic. However, this doesn't necessarily imply that the number of 
marriages increased after Covid because the scatter of the data points in the 
graph demonstrates that the data was potentially measured differently before and 
after 2020. Thus, there may be measuring bias, and the result may be inconclusive.

# References

@opendatatorotno
@thereferencecanbewhatever
@talia
@dplyr